### 2022-01-27 input/experiments.tex
Experiment review until sub section C

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations conducted on PeerSim, a
simulator that allows researchers to evaluate and assess distributed
algorithms in large scale networks~\cite{montresor2009peersim}. All
the code is available on the Github platform at
\mbox{\url{https://github.com/ane-wane/as-cast}}.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution. We set the weight of links between 5 and 15 at random
following a uniform distribution. Weights and latency are different,
hence the first $\alpha$ received by a \process may not be that of its
shortest path. It implies more concurrent operations, hence more
traffic to reach consistent partitioning.

\noindent We evaluate dynamic consistent partitioning. First, we
create 100 partitions one at a time: \processes reach consistent
partitioning before we create each new partition. Second, we remove
every partition one at a time, in the order of their creation, hence
starting from the first and oldest partition that had been added.

@@

\noindent Therefore, the first partition is the most expensive, for $\alpha$'s
must reach every \process which takes time and generate more traffic.
\NAME quickly converges towards consistent partitioning in only 350
milliseconds. The last and $100^{th}$ partition added around 21
seconds is the least expensive. By using scoped broadcast, control
information only reaches a small subset of the whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as \texttt{Add}
operations. Indeed, the top part of the figure shows that after 21
seconds, when the experiment involves removals, traffic includes both
$\alpha$'s and $\delta$'s. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started. %%is already partially triggered and
propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 adds and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead
when there is no operation in the system. \NAME's overhead actually
depends on its usage.

@@

\noindent Figure~\ref{fig:geant} highlights that \NAME operates well
even when \emph{physical} partitions appear. Indeed, the disconnection
of the only inter-continental link existing between the two clusters
either leads to 
\begin{inparaenum}[(i)]
\item additional traffic when the \processes do not have any source in
  their cluster, for \processes need to purge all indexes about the
  remote unreachable source until reaching consistent partitioning; or
\item an already consistent partitioning, for \processes of each
  cluster already target the source in their respective cluster.
\end{inparaenum}

\noindent Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ milliseconds delay corresponding to the link
latency, the cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their cluster.

>>>>

%To answer questions such as: what is the overhead of reaching
%consistent partitioning using \NAME in large scale networks and is
%\NAME relevant in Edge infrastructures where \processes are
%geo-distributed into clusters?
In this section, we discuss the evaluations of \NAME we conducted on top of
PeerSim, a simulator to
evaluate and assess distributed algorithms in large scale
networks~\cite{montresor2009peersim}. All the code is available on the
Github platform at \mbox{\url{https://github.com/ane-wane/as-cast}}.

@@

We build a network comprising 10k \processes. First, we chain
\processes together, then we add another communication link per
\process to another random \process. Since links are bidirectional,
each \process has 4 communication links on average. We set the latency
of links between 20 and 40 ms at random following a uniform
distribution. We set the weight of links between 5 and 15 at random
following a uniform distribution also. Weights and latency are different,
hence the first $\alpha$ received by a \process may not be that of its
shortest path. It implies more concurrent operations, hence more
traffic to reach consistent partitioning.\note{Pour moi ce n'est pas assez claire pourquoi more traffic to reach CP +proposition de reformulation voir tex}
% Weight and latency are different in order to imply more concurrent operations (hence more traffic to reach consistent partitioning): the first $\alpha$ received by a node may not be that of its shortest path.

\noindent To evaluate dynamic consistent partitioning we, first, 
create 100 partitions one at a time: \processes reach consistent
partitioning before we create each new partition. Second, we remove
every partition one at a time, in the order of their creation, hence
starting from the first and oldest partition that had been added.

@@

\noindent Therefore, the first partition is the most expensive, for $\alpha$'s\note{'s pas compris? all $alpha$ sounds better?}
must reach every \process which takes time and generate more traffic.
\NAME quickly converges towards consistent partitioning in only\note{in only... why only? compare to what ? Is it good bad? why?}
% we should give additional elements to explain why it is rather ok to converge in 350ms: maybe by underlining the nb of nodes and the average latency between nodes.
350 milliseconds. The last and $100^{th}$ partition added around 21
seconds is the least expensive. By using scoped broadcast, control
information only reaches a small subset of the whole network.

\noindent Figure~\ref{fig:complexity} also confirms that \NAME's
delete operations are roughly twice as expensive as creation
ones. Indeed, the top part of the figure shows that after 21 seconds,
when the experiment involves removals, traffic includes both
$\alpha$'s and $\delta$'s. The latter aims at removing stale
information and triggering competition while the former aims at
updating shortest paths. As corollary, the convergence time increases,
for $\delta$ messages must reach the partition borders before sound
competitors propagate their partition. It is worth noting that this
delete operation involves concurrency: removals still propagate while
the competition has started.
%%is already partially triggered and propagating.

@@

\noindent Finally, Figure~\ref{fig:complexity} highlights that after
49 seconds, i.e., after the 100 creations and the 100 deletes, \processes
do not generate traffic anymore. Being reactive, \NAME has no overhead \note{can we precise: no overhead related to the indexation updates but heartbeat behind the scene which is crucial?}
when there is no operation in the system. \NAME's overhead actually
depends on its usage.

@@

\noindent Figure~\ref{fig:geant} highlights that \NAME operates well
even when \emph{physical} partitions appear. Indeed, the disconnection
of the inter-continental link existing between the two clusters
either leads to 
\begin{inparaenum}[(i)]
\item additional traffic when the \processes do not have any source in
  their cluster because \processes need to purge all indexes about the
  remote unreachable source until reaching consistent partitioning; or
  %\item an already consistent partitioning as \processes of each
  \item a status quo as \processes of each 
  cluster already target the source in their respective cluster.
\end{inparaenum}

\noindent Finally, Figure~\ref{fig:geant} shows that, when adding back the
inter-continental link, the two clusters can communicate again. In the
experiment involving one source for two clusters, it generates
traffic. After a $200$ milliseconds delay corresponding to the inter-continental link
latency, the cut off cluster starts to communicate $\alpha$ messages
again. Eventually, all \processes belong to the same
partition. However, in the experiment involving one source \emph{per}
cluster, the new link does not trigger noticeable traffic, for
\processes already know their closest source located in their cluster.
